---
title: "LR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LR)
library(bench)
```

## How to use this package

Users need to prepare two data sets as prediction variables(X) and outcome variable(Y) respectively. The former one is a numerical matrix, where each row represents an observation and each column represents a prediction variable (intercept should not be included). The latter is a column vector (or a n by 1 numerical matrix) representing the outcome variable. 

*(1) Fit a simple linear regression model:*

We can obtain the the point estimates, standard errors, t values for partial test, and corresponding p-value of the coefficients of the simple linear regression.

```{r, collapse=TRUE}
y <- as.matrix(state.x77$`Life Exp`)
colnames(y) <- "Life Exp"
x <- as.matrix(state.x77$Murder)
colnames(x) <- "Murder"
SLR.model <- lr(y, x)
print(SLR.model$Coefficents)
```
*(2) Fit a mutiple linear regression model:*

We can obtain the the point estimates, standard errors, t values for partial test, and corresponding p-value of the coefficients of the simple linear regression.

```{r,collapse=TRUE}
y <- as.matrix(state.x77$`Life Exp`)
colnames(y) <- "Life Exp"
x <- as.matrix(state.x77[,c(1:3, 5:8)])
MLR.model <- lr(y, x)
print(MLR.model$Coefficents)
```

*(3) Calculate the 95% confidence interval of $\beta$'s:*

We can get the lower and upper bound of the confidence interval, with default confidence level of 0.95.

```{r, collapse=TRUE}
CI.95 <- lr(y, x, CI = TRUE, CI.level = 0.95)$Confidence_Interval
print(CI.95)
```

*(4) Calculate $R^2$ and adjusted $R^2$ of linear model:*

```{r}
r.square <- lr(y, x)$R_squared[[1]]
adjusted.r.square <- lr(y, x)$R_squared[[2]]
print(r.square)
print(adjusted.r.square)
```

*(5) Calculate the F value for overall F test and the corresponding p-value.*

```{r}
F.stat <- lr(y, x)$F_statistics
print(F.stat)
```
*(6) Use Rcpp to improve efficiency*

```{r}
lr.Rcpp <- lr(y, x, Rcpp = T)
print(lr.Rcpp)
```

### compare my function with "lm()" function
```{r}
X <- matrix(rnorm(500), ncol = 5)
beta <- runif(5)
Y <- X %*% beta + rnorm(100, sd = 0.1)
  
 
compare <- bench::mark(myfun = {
  coefs.actual <- as.vector(lr(Y, X)$Coefficents[, 1])
}, lm.fun = {
   coefs.expected <- as.vector(lm(Y ~ X)$coefficients)
})
summary(compare)
```

### compare cpp function efficiency in my code
```{r}
X <- matrix(rnorm(5000), ncol = 50)
beta <- runif(50)
Y <- X %*% beta + rnorm(100, sd = 0.1)
  
 
compare.Rcpp <- bench::mark(
  myfun.useRcpp = {
  coefs.wRcpp <- as.vector(lr(Y, X, Rcpp = T)$Coefficents[, 1])
}, lm.fun = {
  coefs.noRcpp <- as.vector(lr(Y, X, Rcpp = F)$Coefficents[, 1])
})
summary(compare.Rcpp)
```
we can observe that while we use the Rcpp version of my code, the efficiency will improve a lot.
